### 2019-09-14 README.Rmd
authorship updates
pkgdown fixes

---
output:
  rmarkdown::github_document
bibliography: "README-refs.bib"
---

@@

__Author:__ [Nima Hejazi](https://nimahejazi.org)

@@

&copy; 2017-2018 [Nima S. Hejazi](https://nimahejazi.org)

>>>>

---
output:
  rmarkdown::github_document
bibliography: "inst/REFERENCES.bib"
---

@@

__Author:__ [Nima Hejazi](https://nimahejazi.org) and [Mark van der
  Laan](https://vanderlaan-lab.org)

@@

&copy; 2017-2019 [Nima S. Hejazi](https://nimahejazi.org)
